Chemistry of fossil Pinus pollen and the effect of acetolysis

### 2021-04-07 manuscript.Rmd
mean spectra plotting function

if (file.exists(here("data","output","MFM_spectra.rds"))) {
  MFM = readRDS(here("data","output","MFM_spectra.rds"))
  MFM[MFM$depth=="A4UR_72-74", 'depth'] = "A5UR_72-74" #fixing typo in sample name
  MFM$age = fn_age(MFM$depth)
} else {
  source(here("R","read_data.R"))
  read_data("MFM")
  MFM = readRDS(here("data","output","MFM_spectra.rds"))
}

@@

In this study we investigate the chemistry of fossil pollen to explore three potential sources of chemical alteration: i. the effects of diagenesis, ii. acetolysis and iii. age on pollen chemistry.
We extracted pollen from three sediment cores using density separation to obtain chemically untreated fossil spectra.
The pollen was collected from three different cores in three locations (Germany and Norway), which allows us to examine potential differences in diagenesis on pollen chemistry at different locations.
One replicate of the pollen samples in each core were acetolysed to analyse any changes caused by the strong acid treatment and compared to the untreated replicate.
Each core was sub sampled at different depths to allows us to investigate chemical changes in the pollen with age.
[@noguesbravoCrackingCodeBiodiversity2018]
RQs
i. Differences between cores
ii.i Difference between acetolysed and fossil
ii.ii Difference between fresh and fossil grains.
iii effect of depth/age on chemistry

>>>>

if (file.exists(here("data","output","MFM_spectra.rds"))) {
  MFM = readRDS(here("data","output","MFM_spectra.rds"))
  MFM[MFM$depth=="A4UR_72-74", 'depth'] = "A5UR_72-74" #fixing typo in sample name
  MFM$age = fn_age(MFM$depth)
  MFM[MFM$treatment == "","treatment"] = "SPT"
} else {
  source(here("R","read_data.R"))
  read_data("MFM")
  MFM = readRDS(here("data","output","MFM_spectra.rds"))
}

@@

In this study we investigate the chemistry of fossil pollen to explore three potential sources of chemical alteration: i. the effects of diagenesis, ii. acetolysis and iii. age on pollen chemistry.
We extracted pollen from three sediment cores using density separation to obtain chemically untreated fossil spectra.
The pollen was collected from three different cores in three locations (Germany and Norway), which allows us to examine potential differences in diagenesis on pollen chemistry at different locations.
One replicate of the pollen samples in each core were acetolysed to analyse any changes caused by the strong acid treatment and compared to the untreated replicate.
Each core was sub sampled at different depths to allows us to investigate chemical changes in the pollen with age.

RQs
i. Differences between cores
ii.i Difference between acetolysed and fossil
ii.ii Difference between fresh and fossil grains.
iii effect of depth/age on chemistry
